The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-23 paper/ms.tex
finished maxima subsection

We parameterize the dependency of the linewidth as $W_{1/2}^2 =
W_{1/2,0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{1/2,0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for the

Figure \ref{fig:maximumsvsvelocity} shows the position for the peak
maxima as a function of the rotational velocity $V_{\rm max}$. This
Figure clearly shows that in the case of central distributed
sources there is barely any change with rotational velocity in the
range of explored parameters. However, in the case of
homogeneously emitted sources the maxima position remain close to
constant until beyond some velocity threshold the line becomes single
peaked with $x_{\rm m}=0$ \kms.

The transition to a single peaked line seems to occur in systems
where it is easier for the bulk of the photons to escape with the lowest
number of scatterings possible, allowing them not to move very far
from the center of the line. This might explain how the single peak stage
is easily achieved in the homogeneous source distribution. In this
case there is a fraction of the photons that are inside a photo-sphere
region with $\tau_{H,r}\ll \tau_{H}$ where $\tau_{H,r}$ is the optical
depth from the radius of emission to the sphere's surface. These
conditions allows the photons to escape with much less scatterings
compared to the photons emitted at the very center of the sphere. In
turn, it gives the photons less scatterings to be placed far from the
line center.

Increasing the rotational velocity $V_{\rm max}$ reduces
the optical depth making the photo-sphere region effectively larger,
increasing the number of photons escaping close to the line's
center. In our models we find the following correspondence between the
optical depth $\tau_{\rm H}=\{10^5, 10^6, 10^7\}$ and the transitional
velocities $V_{\rm   trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$
which can only be constrained to be in the range of velocities in the
models that gave a $x_{\rm max}\neq 0$ and $x_{\rm max}=0$.

% No entiendo la restricción!

For the central emission the transition to a single peak is never
completed in the range of explored parameters. The non appearance
of a single peak phase can be in part explained to the absence of a
photo-sphere, as is the case in the homogeneous
distribution. Nevertheless, there is a rise in the intensity at the
line center as the rotational velocity increases. This hints that the
encounters with a non static medium are inefficient in pushing photons
outside the line's center.

In the next sub-section we quantify the number of scatterings and explore
to what extent this is related to the emergence of single peaked emission.

>>>>

We parameterize the dependency of the linewidth as $W_{1/2}^2 =
W_{1/2,0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{1/2,0}$ is the
velocity width in the static case and $\lambda$ is a positive
scalar to be determined as a fit to the data. With this test we want
to know to what extent the new velocity witdth can be expressed as a
quadratic sum of the two relevant velocities in the problem. We find
that for $\lambda = x\pm y$ ($\lambda=x\pm y$) for the central
(homogeneous) sources.

In order to quantify the transition to a single peak we measure the
position for the peak maxima as a function of the rotational
velocity. Our results are presented in Figure
\ref{fig:maximumsvsvelocity} where it is clear that for central
sources there are always two peaks with fixed positions as the rotational
velocity changes. However, in the case of homogeneously emitted
sources the maxima position remain close to constant until some
velocity threshold the line becomes single peaked with $x_{\rm m}=0$
\kms. {\bf By inspection we find that in all cases the transition has
occurred when the rotational velocity is larger than the intrinsic
linewidth OR HALF WIDTH ONCE THE NUMBERS ARE FIXED?}.

One possible explanation for the emergence of the single peak in the
homogeneous source systems is that some photons close to the surface
(a sort of photosphere) can escape with a low number of scatterings,
allowing them to stay close to the line's center. Increasing the
rotational velocity $V_{\rm max}$ reduces the optical depth making the
photosphere region effectively larger, increasing the number of
photons escaping close to the line's center.

However, for the central emission the transition to a single peak is
never completed in the range of explored parameters. The absence
of a single peak phase could be partially explained by the absence of a
photosphere, in this case the average number of scatterings to escape
should remain close to constant as the rotational velocity
increases. The rise in intensity at the line's center could instead
mean that the scattering in a medium with bulk motion are inefficient
in driving photons outside that frequency region.

In order to explore our interpretation for these two scenarios we now 
quantify the effect of rotation on the number of scatterings.
